---
title: "myProject"
author: "Shruti Wali"
date: "December 31, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##Requirements:
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!


- Have used time series dataset (austres) from library datasets.
- Numbers (in thousands) of Australian residents measured quarterly from March 1971 to March 1994.
- The object is of class “ts”.


```{r, echo = TRUE}
library(plotly)

library(datasets)
library(zoo)

data(austres)
library(reshape2)
df <- data.frame(value=as.matrix(austres), date=as.Date(as.yearmon(time(austres))))
```
## Slide with Plot

```{r}
f <- list(
  family = "Times New Roman, monospace",
  size = 18,
  color = "#888ggf"
)

x <- list(
  title = "Year",
  titlefont = f
)
y <- list(
  title = "Numbers (in thousands) of Australian Residents",
  titlefont = f
)

plot_ly(df, x = ~as.Date(date), y = ~value, type = 'scatter', 
        mode = 'lines') %>% layout(xaxis = x, yaxis = y)
```

